Trends of downward SDR in Thessaloniki

### 2023-05-05 Article.Rmd
Commit 2023-05-05 21:17

<!-- basic concepts -->
The approach of our method to characterize the sky conditions and the definition of each sky condition has some ......μη αντικειμένικότητα

>>>>

<!-- basic concepts -->
Our method to characterize the sky conditions and the definition of each sky condition has some subjectivity. The algorithm was calibrated with the main focus to identify the presence of clouds on the sky dome, although there are marginal cases that there will be false positives or false negateives.
